### 2021-02-09 sections/method.tex
Updates from Tim

Some galaxies in \citet{2020arXiv200610450L} were shown to volunteers a second time in a repeat validation subset to create a second aggregate model used to test internal consistency. We combine the 30 classifications of galaxies in this validation subset with the 30 original classifications. Clustering of drawn spiral arms and cleaning of points was then performed as detailed in \citet{2020arXiv200610450L}. We remove any galaxies for which no spiral arms were identified, resulting in a hierarchical data structure of 139 galaxies, 261 spiral arms and 239,947 points.

>>>>

Some galaxies in \citet{2020arXiv200610450L} were shown to volunteers a second time in a repeat validation subset to create a second aggregate model used to test internal consistency. We combine the 30 classifications of galaxies in this validation subset with the 30 original classifications. Clustering of drawn spiral arms and cleaning of points was then performed as detailed in \citet{2020arXiv200610450L}. We remove any galaxies for which no spiral arms were identified, resulting in a hierarchical data structure of {\bf 129 galaxies, 247 spiral arms and 238,433 points}.
